Title Goes Here

### 2020-04-24 analysis/paper/paper.Rmd
trimmed raw data

#need to figure out how to read the file inside the project
landmarks <- read.tps(here("analysis/data/raw_data/A_BG_2.tps"))

@@

#trim the name of each artifact.
df_sitename <- df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

# artifacts from SYG6 site
library(stringr)
SYG6_df <- 
  df %>% 
  filter(str_detect(files, "SYG6"))

SYG6_df_sitename <- SYG6_df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

# artifacts from SYG_1 site
library(stringr)
SYG_1df <- 
  df %>% 
  filter(str_detect(files, "SYG_1"))

SYG_1df_sitename <- SYG_1df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

SYG_4 site data and analysis

# artifacts from SYG_4 site
library(stringr)
SYG_4df <- 
  df %>% 
  filter(str_detect(files, "SYG_4"))

SYG_4df_sitename <- SYG_4df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

#list of all attributes without ID
SYG_4DF <- SYG_4df[,1:7]

#simpler way to calculate Correlataion, you can use
SYG_4cor <- cor(SYG_4DF)

#a scatterplot matrix of Correlation
pairs(SYG_4DF)

cplot_SYG_4 <- corrplot(SYG_4cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

# CV
map_df(SYG_4DF, cv)

SYG_4PCA <- prcomp(SYG_4DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG_4xx_pca <- 
SYG_4df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG_4xx_pca1 <- 
  data.frame(SYG_4xx_pca$x,
             stage = as.factor( SYG_4df_sitename$SPstage.Stage[SYG_4df_sitename$SPstage.Stage !=1]))

#plot for both stage
SYG_4gg_stage <- 
ggplot(SYG_4xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

fviz_pca_var(SYG_4xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

SYG_4PC1_v <- fviz_contrib(SYG_4xx_pca, choice = "var", axes = 1, top = 7)
SYG_4PC2_v <- fviz_contrib(SYG_4xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG_4PC1_v, SYG_4PC2_v, nrow =1)
```

Correlations for each site
```{r}
par(mfrow=c(1,3))
cplot_SYG6 <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
cplot_SYG_1 <- corrplot(SYG_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
cplot_SYG_4 <- corrplot(SYG_4cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

>>>>

#need to figure out how to read the file inside the project
landmarks <- read.tps(here("analysis/data/raw_data/BG_0_2.tps"))

@@

#trim the name of each artifact.
df_sitename <- df %>% 
  mutate (files = str_remove_all(files, "_.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

# artifacts from SYG6 site: now it has two layers, two phases
library(stringr)
SYG6_df <- 
  df %>% 
  filter(str_detect(files, "SYG6"))

SYG6_df_sitename <- SYG6_df %>% 
  mutate (files = str_remove_all(files, "_.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

# artifacts from SYG1 site
library(stringr)
SYG_1df <- 
  df %>% 
  filter(str_detect(files, "SYG1"))

SYG_1df_sitename <- SYG_1df %>% 
  mutate (files = str_remove_all(files, "_.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

Correlations for each site
```{r}
par(mfrow=c(1,2))
cplot_SYG6 <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
cplot_SYG_1 <- corrplot(SYG_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
